MSE and dynamic state variable model with sigma function

### 2018-05-14 doc/MSE_MAR_18.tex
Added figure with distributions
We need to check if legend is correct (i.e. high and low abundances are correctly coloured for the two species.
Code (not included in order not to change model code):
setEPS()
postscript("distributions.eps")
par(oma=c(0,0,0,0), mar=c(4.1, 4.1, 3.1, 1.1))
split.screen( rbind(c(0, .8,0,1), c(.8,1,0,1)))
split.screen(c(2,1), screen=1)-> ind
screen( ind[1])

image(matrix(round(aperm(pop1[,5,,],c(2,1,3))), ncol=2), col=gray((0:64)/64), axes=F, main= "Species 1", ylab="Area" )
box()
axis(2,at= seq(0.,1,1),labels= c("S","N"), las=1)
axis(1,at= seq(0.,0.75,0.25),labels=

\begin{figure}[!ht]
\centering
\includegraphics[width=.69\textwidth]{Figures/prices.eps} 
\caption{Lengths and prices of the species}
\end{figure}

@@

To mimic spatially heterogeneous fish populations in a mixed fishery where fishers make sequential choices on fishing areas and discarding patterns, the model was divided into a 'north' and 'south' area, and six fishing seasons per year (Table \ref{t:fishery}). There were two fish species in the model, both of which are caught by the fishery. The annual number of newborns is equal for the two species, and arbitrarily set to 400 per year. The species differ with respect to their nursery grounds: all individuals of species 1 are born in the southern area, while all individuals of species 2 are born in the northern area. The maximum age that any individual can reach was 4 years old. During their life, individuals grew in length towards the asymptotic length, which was 50 cm. for both species. Conversion from length to weight was also equal for the two species (Table \ref{table:kysymys}).
Migration was parameterized so that a gradual diffusion occured between the two areas, euqal to 20 percent of the difference in abundance. 
 A 20 \% constant migration during any season was set between areas. The migration in population numbers ($M_i (a, s, im, em)$) was thus the proportion ($P (a, y, s, i, em, im)$) of the population available or vulnerable to fishing after migration occurs:

In the case study, age-dependent catchability links the population biomassed to the catches in the fishery, and it is thus one of the crucial parameters determing the interaction between the two. In the case study, this age-dependent catchability $q_i (a)$ was assumed independent of age $a$, and equal for the two species.

 A 20 \% constant migration during any season was set between areas. The migration in population numbers ($M_i (a, s, im, em)$) was thus the proportion ($P (a, y, s, i, em, im)$) of the population available or vulnerable to fishing after migration occurs:

 was set to $3 x 10^3$ Euro day\textsuperscript{-1}. These high fines combined with an assumed 100\% detection of exceeding quotas resulted in model results in which fishers comply with quota regulations.

We used mean prices of 150 Euro kg\textsuperscript{-1} for both species.

Mortality from natural causes such as predation, diseases, and scenesens was assumed to be negligible in comparison. Althought such absence of natural mortality impossible in reality, one could argue that the model thus mimiced long-lived species.

\subsection{Endogenously determined quotas}
\label{sec2.3}

The two management strategies we considered differ by the formulae used to determine exploitation rates (HCR). These manegemet strategies were chosen such that, if  the  management  model  was  the  correct  model  of  reality,  the corresponding  equilibrium  state  of  the  system  would  meet  the  objective  of  the  plan. For this purpose, each strategy was implemented after a period where the fishery was unmanaged, by meaned with unconstrained quota for both species.

>>>>

\begin{figure}[!ht]
\centering
\label{f:prices}
\includegraphics[width=.69\textwidth]{Figures/prices.eps} 
\caption{Lengths and prices of the species}
\end{figure}

@@

To mimic spatially heterogeneous fish populations in a mixed fishery where fishers make sequential choices on fishing areas and discarding patterns, the model was divided into a 'north' and 'south' area, and six fishing seasons per year (Table \ref{t:fishery}). There were two fish species in the model, both of which are caught by the fishery. The annual number of newborns is equal for the two species, and arbitrarily set to 400 per year. The species differ with respect to their nursery grounds: all individuals of species 1 are born in the southern area, while all individuals of species 2 are born in the northern area. The maximum age that any individual can reach was 4 years old. During their life, individuals grew in length towards the asymptotic length, which was 50 cm (Figure \ref{f:prices}). for both species. Conversion from length to weight was also equal for the two species (Table \ref{t:fishery}). Migration was parameterized so that a gradual diffusion occured between the two areas, euqal to 20 percent of the difference in abundance. For the unfished situation this led to a clear segregation of the younger ages over the two areas, while the older ages were equally distributed over the two areas  (Figure \ref{f:distributions}). Mortality from natural causes such as predation, diseases, and scenesens was assumed to be negligible, and $M_i$ set to 0.0001. Althought such absence of natural mortality impossible in reality, one could argue that the model thus mimiced long-lived species.

Age-dependent catchability links the population biomasses to the catches in the fishery, and is thus one of the crucial parameters determing the interaction between the two. In the case study, this age-dependent catchability $q_i (a)$ was assumed independent of age $a$, and equal for the two species.

The mean prices for the two species were set to 150 euro per ton, ranging between 63 euro per ton for the youngest age and and 238 ton for the oldest age. The fines for overshooting the quota was set  to 500 euro per ton. These high fines combined with an assumed 100\% detection of exceeding quotas resulted in model results in which fishers comply with quota regulations.

\subsection{Management procedure}
\label{sec2.3}
The fisheries model 
The two management strategies we considered differ by the formulae used to determine exploitation rates (HCR). These manegement strategies were chosen such that, if  the  management  model  was  the  correct  model  of  reality,  the corresponding  equilibrium  state  of  the  system  would  meet  the  objective  of  the  plan. For this purpose, each strategy was implemented after a period where the fishery was unmanaged, by meaned with unconstrained quota for both species.

\begin{figure}[!ht]
\centering
\label{f:distributions}
\includegraphics[width=.69\textwidth]{Figures/distributions.eps} 
\caption{Distribution of the two species over the areas as a function of age in unfished situation}
\end{figure}
